Feature Selection and Classification of \\ Spam on Social Networking Sites

### 2012-05-09 docs/paper/paper.tex
reorg
typo

\begin{itemize}
\item \textbf{Advance fee fraud}, including inheritance, lotter, visa and customs-clearance scams
\item \textbf{Romance scams}, including ``mail-order bride" and military scams
\item \textbf{Sexual solicitation}
\item \textbf{Ads for porn sites}, primarily adult webcam and live chat sites.
\item \textbf{Ads for miscellaneous external sites}, often other SNSs
\item \textbf{Money muling}, often in the guise of high-paying ``stay-at-home" jobs or ``mystery" shopping
\item \textbf{Begging \& gift requests}
\item \textbf{Business proposals}
\end{itemize}

@@

\section{Classifiers \& Results}

@@

@@

%intro to svms

\subsection{SVM Results}

Our initial results using the Pegasos SVM solver included in ScalaNLP were lower than expected. The 
classifier trained on the bag-of-words feature set (22k messages) yielded a 77\% mean accuracy 
over 10-fold cross-validation. The addition of expert features actually decreased this accuracy to 
51\%.

>>>>

\begin{itemize}
\item \textbf{Advance fee fraud}, including inheritance, lottery, visa and customs-clearance scams
\item \textbf{Romance scams}, including ``mail-order bride" and military scams
\item \textbf{Sexual solicitation}
\item \textbf{Ads for porn sites}, primarily adult webcam and live chat sites.
\item \textbf{Ads for miscellaneous external sites}, often other SNSs
\item \textbf{Money muling}, often in the guise of high-paying ``stay-at-home" jobs or ``mystery" shopping
\item \textbf{Begging \& gift requests}
\item \textbf{Business proposals}
\end{itemize}

@@

\section{Classifiers}

@@

\section{Performance \& Results}

@@

\subsection{SVM Results}
Our initial results using the Pegasos SVM solver included in ScalaNLP were lower than expected. The 
classifier trained on the bag-of-words feature set (22k messages) yielded a 77\% mean accuracy 
over 10-fold cross-validation. The addition of expert features actually decreased this accuracy to 
51\%.
